Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-02-24 ms/ms08_figures.tex
MS figurex

\begin{figure}[h!]
    %
    \centering
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/violin.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/violin.png}
    \end{subfigure}
    %
    \caption{} \label{fig:gwas_egene_etisue_per_variant}
    %
\end{figure}

@@

\begin{figure}[h!]
    \centering
    %
    \begin{subfigure}[]{.48\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.48\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}
    %
    \caption{}
    %
\end{figure}

>>>>

\begin{figure}[h!]
    %
    \centering
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.45\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
    \end{subfigure}
    %
    \caption{} \label{fig:gwas_egene_etisue_per_variant}
    %
\end{figure}

@@

\begin{figure}[h!]
    \centering
    %
    \begin{subfigure}[]{.48\textwidth}vep.png
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.48\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
    \end{subfigure}
    %
    \caption{}
    %
\end{figure}
